07-logistic_regression

### 2019-02-26 journals/07-logistic_regression/07-logistic_regression.Rmd
journal 07

@@

@@

  # Apply explain
  explain_mains <- explain(x = hamby224_test %>%
                             select(rf_features) %>% 
                             na.omit(), 
                           explainer = logistic_mains_lime, 
                           n_labels = 1,
                           n_features = 3)

@@

  # Apply explain
  explain_inters2 <- explain(x = hamby224_test %>%
                               select(rf_features) %>% 
                               na.omit(), 
                             explainer = logistic_inters2_lime, 
                             n_labels = 1,
                             n_features = 3)

@@

  # Apply explain
  explain_inters3 <- explain(x = hamby224_test %>%
                               select(rf_features) %>% 
                               na.omit(), 
                             explainer = logistic_inters3_lime, 
                             n_labels = 1,
                             n_features = 3)

>>>>

  # Set a seed
  set.seed(20190226)

@@

The results as computed by caret on the training data are shown below for the three logistic regression models. The accuracy shows that the models with two way interactions performs the best on the training data.

```{r}
# Results from the models
data.frame(model = c("mains", "inters2", "inters3")) %>%
  bind_cols(bind_rows(logistic_mains$results, logistic_inters2$results, logistic_inters3$results))
```

The AICs from the models are shown below. The model with three way interactions performs the best based on AIC.

```{r}
AIC(logistic_mains$finalModel)
AIC(logistic_inters2$finalModel)
AIC(logistic_inters3$finalModel)
```

I also want to know how the models perform on the test data. The models are used to make predictions on the test data and the MSEs are computed for each model. These are shown in the table below. The model with main effects only has the smallest MSE. I am guessing that the other models are overfitting.

```{r}
data.frame(mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
           inters2 = predict(logistic_inters2, hamby224_test %>% select(rf_features)),
           inters3 = predict(logistic_inters3, hamby224_test %>% select(rf_features))) %>%
  summarise_at(vars(mains, inters2, inters3), 
               function(pred, obs) sum((as.logical(pred) - obs)^2) / n(),
               obs = hamby224_test %>% select(samesource) %>% na.omit())
```

@@

  # Apply explain
  explain_mains <- explain(x = hamby224_test %>%
                             select(rf_features) %>% 
                             na.omit(), 
                           explainer = lime_mains, 
                           n_labels = 1,
                           n_features = 3)

@@

  # Apply explain
  explain_inters2 <- explain(x = hamby224_test %>%
                               select(rf_features) %>% 
                               na.omit(), 
                             explainer = lime_inters2, 
                             n_labels = 1,
                             n_features = 3)

@@

  # Apply explain
  explain_inters3 <- explain(x = hamby224_test %>%
                               select(rf_features) %>% 
                               na.omit(), 
                             explainer = lime_inters3, 
                             n_labels = 1,
                             n_features = 3)
